### 2017-11-06 Draft2/Appending.Growth.tex
Some work

\begin{lemma}
	$\VarUseful = O(\log n)$.
\end{lemma}

@@

@@

I now approximate this expression using $\sim$. First, I approximate $k$ using big-O:

\begin{align*}
k &= \lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil\\
O(k) &= O(\log n)
\end{align*}

Now, the $k$-term disappears when using $\sim$ to approximate $\FuncWrites(n)$, leaving just $n$:

\begin{align*}
\FuncWrites(n) &\sim n + \FuncWrites(k)\\
&= n + O(\log n)\\
&\sim n
\end{align*}

% Should this be C(n) instead of C?
The space function for $n$ $\FuncAppend$ calls on a growth array is denoted $\FuncSpace(n)$. Since growth arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$. $\FuncSpace(n)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail. Thus the space the tail allocates must also be determined.

I determined in [...] that if $n$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil$. Since the tail is a dynamic array, it allocates $\FuncSpace(k)$ space, where $\FuncSpace$ is the space function of the tail. Through a similar method to [...] it can be shown $O(\FuncSpace(k)) = O(k) = O(\log n)$. Then % TODO: P-analysis should come after the explicit formula.

\begin{align*}
\FuncSpace(n) \sim 2^{\lceil \log_2 n \rceil} = O(n)
\end{align*}

>>>>

\begin{lemma}
\label{lem:VarUsefulIsOLogN}
	$\VarUseful = O(\log n)$.
\end{lemma}

@@

Now when $\FuncWrites(n)$ is approximated with $\sim$, the $\FuncWritesTail(\VarUseful)$ term disappears:
\begin{align*}
\FuncWrites(n) &= n + \FuncWritesTail(\VarUseful) = n + O(\VarUseful) = n + O(\log n) \sim n
\end{align*}

Unlike dynamic arrays, growth arrays never throw away buffers. This means that if the current capacity is $c$, then the total length of buffers allocated to store items is also $c$. Typically, however, $\FuncSpace(n) > c$. This is because growth arrays not only store items in buffers, they also store \textbf{references} (or \textbf{pointers}) to the buffers holding the items, in the tail. Thus, the space the tail allocates must also be considered.

We established in [lemma] that $\VarNumItemsTail = \VarUseful$. Then since $\VarCapacitySeq_\VarUseful$ is the space needed to hold items, and $\FuncSpaceTail(\VarUseful)$ is the space the tail needs to hold references, the formula for $\FuncSpace(n)$ is
\begin{align*}
\FuncSpace(n) = \VarCapacitySeq_\VarUseful + \FuncSpaceTail(\VarUseful)
\end{align*}
I now wish to approximate this using $\sim$. First, note that since $\VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$, it follows from Lemma \ref{lem:ToVarUsefulPowerBounds} that $n \FluteLeq \VarCapacitySeq_\VarUseful \FluteLess \VarGrowthFactor{n}$. Since $n$ and $\VarGrowthFactor{n}$ are both $O(n)$, [the squeeze theorem] implies that $\VarCapacitySeq_\VarUseful = O(n)$.

Now, consider the ratio $\lim_{n \to \infty} \left( \FuncSpaceTail(\VarUseful) / \VarCapacitySeq_\VarUseful \right) = O(\log n) / O(n) = O({\log n} / {n}) = 0$. Because it is $0$, from \ref{thm:RemovesLowerOrderTerms} we may conclude
\begin{align*}
\FuncSpace(n) = \VarCapacitySeq_\VarUseful + \FuncSpaceTail(\VarUseful) \sim \VarCapacitySeq_\VarUseful
\end{align*}

@@

Using Lemma \ref{lem:VarUsefulIsOLogN} again, $\FuncSpaceTail(\VarUseful) = O(\VarUseful) = O(\log n)$. Similarly to before, the $\FuncSpaceTail(\VarUseful)$ term vanishes under $\sim$:
\begin{align*}
\FuncSpace(n) \sim ... + O(\log n) = ...
\end{align*}

### 2017-11-06 Draft2/FieldsProperties.tex
Lists
Some work

\begin{itemize}
	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. It returns a dynamic array of buffers that have already been filled. This can be thought of as a two-dimensional array.
	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold without resizing.
\end{itemize}

>>>>

\begin{itemize}
	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. \textbf{Important note: The tail is a dynamic array.} It returns a \textit{dynamic array} of references to buffers that are already filled with items. The tail can be thought of as a two-dimensional array.\\
	{\HdrNote} It may seem strange for a growth array to use the very data structure it is replacing. As shown in Lemma \ref{lem:VarUsefulIsOLogN}, however, only $O(\log n)$ many references are appended to the tail. Thus, the extra copying and allocations the tail performs is minuscule compared to other work done by the growth array.
	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold without resizing.
\end{itemize}
